Adopting agile in the large: motivations, success factors and challenges

### 2013-01-26 tex/article.tex
Stepwise adoption as success factor
Author bias because author is in organization

@@

The papers included in this study were mostly experience reports with no reported
research method. Some papers were of low quality, but they were included as our
aim was to give a view of the topic that is broader and inclined towards practice.

>>>>

        \raggedright\rule{0pt}{0.4cm}Stepwise adoption  &
            Piloting [S4, S6, S10, S11, S26, S28, S30]\newline
            Adoption spreads gradually [S15, S22, S27, S29]\\

@@

The papers included were mostly experience reports with no reported research
method. Most authors were in the described organizations, so author bias should
be expected. Some papers were of low quality, but were included as our aim was
to give a view of the topic that is broader and inclined towards practice.
